Sweep A - general experiment analysis.

### 2018-03-07 voltagebudget/analysis/sweep_A_analysis.Rmd
update vis

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  ggplot(aes(x=As, y=V_osc, color=freq)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

>>>>

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  ggplot(aes(x=As*1e9, y=V_osc, color=freq)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```

```{r, fig.width=1.5, fig.height=1.5}
results %>% 
  ggplot(aes(x=As*1e9, y=V_comp, color=freq)) +
  geom_line() + 
  theme_classic() +
  scale_colour_brewer(palette="Greens", guide=guide_legend(nrow=3)) +
  theme(legend.position="bottom") 
```
